ARGoS-Blockchain interface

### 2020-09-04 article.tex
upd

The following setup steps describe the installation using Linux as
operating system.

\subsection{Requirements}
\begin{itemize}
\item Sufficient disk space (at least 16 GB)
\item Docker 
\item ARGoS\footnote{\url{https://github.com/ilpincy/argos3}} and the
  ARGoS e-puck robot
  plugin\footnote{\url{https://github.com/demiurge-project/argos3-epuck}}
  (carefully read the instructions on the respective respositories)
\end{itemize}

@@

\item Obtain the source code for the ARGoS module.
\begin{verbatim}
git clone https://github.com/Pold87/robot-swarms-need-blockchain"
\end{verbatim}
\end{enumerate}

@@

\begin{verbatim}
$ docker build -t mygeth .
$ docker swarm init
\end{verbatim}
% New item
\item Set the ARGoS folder in the file \verb|start_network.sh|.

\begin{verbatim}
$ nano ../local_scripts/start_network
ARGOSFOLDER="/home/vstrobel/software/interface/robot-swarms-need-blockchain"
\end{verbatim}
% TODO: Run script with NUMROBOTS=0
\end{enumerate}
\subsection{Installation --- Module~2: ARGoS module}

\item Compile the ARGoS code.
\begin{verbatim}
$ cd /home/vstrobel/software/interface/robot-swarms-need-blockchain/
$ mkdir build/
$ cd build/
$ cmake ..
$ make
\end{verbatim}

@@

\begin{verbatim}
$ cd ..
$ nano global_config.sh
DOCKERBASE='/home/vstrobel/Documents/docker-geth-network/'
\end{verbatim}

\item In order to be able to mine, you need to create the DAG datasets as
follows (the creates files require approximately 2~GB disk space and
the execution of the script can take take several minutes):

\begin{verbatim}
cd local_scripts/
bash create_dag.sh
\end{verbatim}  
\end{enumerate}

@@

Usually, the network is created when a swarm robotics experiment is
started, using one of the start scripts in
\url{https://github.com/Pold87/robot-swarms-need-blockchain}.

However, you can also start the Ethereum network without ARGoS, using
the following command:

\begin{verbatim}
bash local_scripts/start_network.sh <number of nodes>
\end{verbatim}

>>>>

The following setup steps describe the installation of the
ARGoS-Blockchain interface using Linux as operating system.

\subsection{Requirements}
\begin{itemize}
\item Sufficient disk space (at least 16 GB)
\item Docker 
\item ARGoS\footnote{\url{https://github.com/ilpincy/argos3}} and the
  ARGoS e-puck robot
  plugin\footnote{\url{https://github.com/demiurge-project/argos3-epuck}}
  (see installation instructions below)
\end{itemize}

\subsection{Installation of ARGoS and the ARGoS e-puck plugin}

This section briefly describes the setup of ARGoS and the ARGoS e-puck
plugin. Please carefully read the README files of the respective
respositories for more information.

1. Obtain the source code of both repositories

\begin{verbatim}
$ git clone https://github.com/ilpincy/argos3.git
$ git clone https://github.com/demiurge-project/argos3-epuck.git
\end{verbatim}

2. Install the dependencies.

\begin{verbatim}
$ sudo apt-get install cmake libfreeimage-dev libfreeimageplus-dev \
  qt5-default freeglut3-dev libxi-dev libxmu-dev liblua5.3-dev \
  lua5.3 doxygen graphviz graphviz-dev asciidoc
\end{verbatim}

2. Build and install ARGoS system-wide.
\begin{verbatim}
$ cd argos3/
$ mkdir build
$ cd build
$ cmake ../src
$ make
$ make doc
$ sudo make install
\end{verbatim}

3. Build and install the ARGoS-epuck plugin.

\begin{verbatim}
$ cd ../../argos3-epuck/
$ mkdir build
$ cd build
$ cmake ../src
$ make
$ sudo make install
\end{verbatim}

@@

\item Obtain the source code for the ARGoS module.
\begin{verbatim}
$ git clone https://github.com/Pold87/robot-swarms-need-blockchain
\end{verbatim}
\end{enumerate}

@@

\begin{verbatim}
$ docker build -t mygeth .
$ docker swarm init
\end{verbatim}
% New item
\item Set the ARGoS folder in the file \verb|global_config_blockchain.sh|.

\begin{verbatim}
$ nano ../local_scripts/global_config_blockchain.sh
ARGOSFOLDER="/home/vstrobel/software/interface/robot-swarms-need-blockchain"
\end{verbatim}

\item In order to be able to mine, you need to create the DAG
  datasets. Creating the files requires approximately 2~GB disk space
  and the execution of the script can take take several minutes.

\begin{verbatim}
cd local_scripts/
bash create_dag.sh
\end{verbatim}

\end{enumerate}
\subsection{Installation --- Module~2: ARGoS module}

\begin{enumerate}
\item Compile the ARGoS code.
\begin{verbatim}
$ cd /home/vstrobel/software/interface/robot-swarms-need-blockchain/
$ mkdir build/
$ cd build/
$ cmake ..
$ make
\end{verbatim}

@@

\begin{verbatim}
$ cd ..
$ nano global_config.sh
DOCKERBASE='/home/vstrobel/Documents/docker-geth-network/'
\end{verbatim}
\end{enumerate}

Usually, the network is created when a swarm robotics experiment is
started, using one of the starter scripts in the folder
\verb|robot-swarms-need-blockchain/starters/|. Start with a plain
experiment to see if the installation was succesful. The command needs
to be executed from the base folder of the ARGoS part of the
blockchain interface.

\begin{verbatim}
$ bash starters/1_Plain.sh 3
\end{verbatim}

You can also start the Ethereum network without ARGoS, using
the following command:

\begin{verbatim}
$ bash local_scripts/start_network.sh <number of nodes>
\end{verbatim}

@@
